Title of the Master Thesis

### 2015-10-17 Master Thesis/synopsis.tex
Clarify

\paragraph{} Let $k$ and $k'$ be the algebraic closures of $\mathbb{Q}$ in $K$ and $K'$ respectively, and let $\overline{k}$ and $\overline{k'}$ be the algebraic closure of $k$ and $k'$ in $\overline{K}$ and $\overline{K'}$ respectively.

Let $X$ and $X'$ be the unique smooth projective curve over $k$ and $k'$ with function field $K$ and $K'$ respectively. We identify the set of closed points $X_0$ of $X$ with the set of valuations $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ with $\operatorname{char} k(v)=0$ and similarly identify $X'_0$ with the corresponding subset of $\operatorname{Spv}_\text{d}^{(1)}(K')$.

@@

\begin{lemma}\label{5.4}
Let $S\subset X_0$ be admissible. Then there exists a finite subset $T\subset X_0\setminus S$ such that the following map is injective:
\[ r_{S,T}:K^S \to\prod_{P\in T}k(P)^\times,\ x\mapsto(r_P(x))_{P\in T} \]
In this case, $\operatorname{coker}(r_{S,T})$ is free-by-finite.
\end{lemma}

\begin{definition}
For each admissible $S\subset X_0$ we can find a finite subset $T\subset X_0\setminus S$ such that both $r_{S,T}$ and $r_{S',T'}$ are injective. Such a $T$ will be called $S$-\textit{admissible} and $(S,T)$ is called \textit{admissible pair}.
\end{definition}

>>>>

\paragraph{} Let $k$ and $k'$ be the algebraic closures of $\mathbb{Q}$ in $K$ and $K'$ respectively, i.e. the constant fields of $K$ and $K'$, and let $\overline{k}$ and $\overline{k'}$ be the algebraic closure of $k$ and $k'$ in $\overline{K}$ and $\overline{K'}$ respectively.

Let $X$ and $X'$ be the unique smooth projective curves over $k$ and $k'$ with function field $K$ and $K'$ respectively. We identify the set of closed points $X_0$ of $X$ with the set of valuations $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ with $\operatorname{char} k(v)=0$ and similarly identify $X'_0$ with the corresponding subset of $\operatorname{Spv}_\text{d}^{(1)}(K')$.

@@

\begin{lemma}\label{5.4}
Let $S\subset X_0$ be admissible and $P_0\in X_0\setminus S$. Then there exists a finite subset $T\subset X_0\setminus S$ with $P_0\in T$ such that the following map is injective:
\[ r_{S,T}:K^S \to\prod_{P\in T}k(P)^\times,\ x\mapsto(r_P(x))_{P\in T} \]
In this case, $\operatorname{coker}(r_{S,T})$ is free-by-finite.
\end{lemma}

\begin{remark}
For each admissible $S\subset X_0$ and $T_1\subset X_0\setminus S$ with injective $r_{S,T_1}$ we also have the injectivity of $r_{S,T_2}$ for every $T_2 \supset T_1$. Therefore,  we can find a finite subset $T\subset X_0\setminus S$ such that both $r_{S,T}$ and $r_{S',T'}$ are injective. Such a $T$ will be called $S$-\textit{admissible} and $(S,T)$ is called \textit{admissible pair}.
\end{remark}
